Halo alignments with large scale tidal and velocity fields

### 2013-04-12 paper/main.tex
new two last figures

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}
\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jVWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jTWeb.ps}
\caption{Median of the angular momentum for the two web  and the two grid resolution.}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}
\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T1.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T2.ps}
\includegraphics[width=0.30\textwidth]{../plot2/J/512_J_T3.ps}
\caption{Angular momentum alignment with the Tweb for $512^3$ grid resolution.}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jVWeb.ps}
\includegraphics[width=0.30\textwidth]{../plot2/Mass/jTWeb.ps}
\caption{Median of the angular momentum for the two web  and the two grid resolution.}
\end{figure*}

@@

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T1.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T2.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Vel/512_vel_T3.ps}
%\caption{Peculiar velocity alignment with the Tweb for $512^3$ grid resolution.}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vVWeb.ps}
%\includegraphics[width=0.30\textwidth]{../plot2/Mass/vTWeb.ps}
%\caption{Median of the peculiar velocity for the two web  and the two grid resolution.}
%\end{figure*}

\begin{figure*}
\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_256.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_256.ps}
\caption{From top to bottom: Shape, J, velocities. 256 resolution. Left Tweb, right Vweb}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.35\textwidth]{../tmp/Type/T_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/V_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JT_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/JV_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vT_Web_512.ps}
\includegraphics[width=0.35\textwidth]{../tmp/Type/vV_Web_512.ps}
\caption{From top to bottom: Shape, J, velocities. 512 resolution. Left Tweb, right Vweb}
\end{figure*}

Possible conclusion. Prolateness follow concentration. In the Tweb Angular momentum alignment is influenced by spin at higher masses. In the Vweb angular momentum alginment is influenced by all factors. In the peculiar velocity alginment only spin seemss to have an effect.
